### 2020-11-24 Thesis-Chapter2-Background.tex
Updates based on presentation feedback

One can also define two major cryptographic applications---securing \acf{DIM} and \acf{DAR}. Each application is a
different problem that results in different solutions. \Ac{DIM} typically uses long-lived \ac{asym-crypto} keys to
perform authentication and establish short-lived \ac{sym-crypto} session keys; the session keys perform the actual
encryption of the data in transit. Two important properties of \ac{DIM} encryption protocols are \ac{forward-secrecy}
and \ac{replay-protection}. \Ac{forward-secrecy} ensures that a leaked private key or session key does not compromise
any other private key or session key; \ac{replay-protection} ensures that messages cannot be replayed by an
attacker without detection \cite{bellovin_thinking_2016}. \Ac{E2EE} for instant messaging services is an example of
encryption for \ac{DIM}.

@@

\paragraph*{``Security vs. Security''} The relationship between security and privacy is sometimes viewed as
antagonistic, an assumption implicit in in the ``nothing-to-hide'' argument, but discussions in recent years have shown
that the debate is more about ``Security vs. Security'' than ``Security vs. Privacy''
\cite{stalla_bourdillon_privacy_2014}. In this context, there are two types of security: public security, the pursuit of
law enforcement, and cybersecurity, the pursuit of the technical community. Both sides of the debate have by now
acknowledged that privacy and public security are not always in conflict, and in fact \ac{EA}'s effects on public
security vs. cybersecurity---which in return affects public security---may be more important \cite{schneier_2019}.

@@

@@

>>>>

One can also define two major cryptographic applications---securing \acf{DIM} and \acf{DAR}. Each application is a
different problem that results in different solutions. \Ac{DIM} typically uses long-lived \ac{asym-crypto} keys to
perform authentication and establish short-lived \ac{sym-crypto} session keys; the session keys perform the actual
encryption of the data in motion. Two important properties of \ac{DIM} encryption protocols are \ac{forward-secrecy} and
\ac{replay-protection}. \Ac{forward-secrecy} ensures that a leaked private key or session key does not compromise any
other private key or session key; \ac{replay-protection} ensures that messages cannot be replayed by an attacker without
detection \cite{bellovin_thinking_2016}. \Ac{E2EE} for instant messaging services is an example of encryption for
\ac{DIM}.

@@

\paragraph*{``Security vs. Security''} The relationship between security and privacy is sometimes viewed as
antagonistic, an assumption implicit in the ``nothing-to-hide'' argument, but discussions in recent years have shown
that the debate is more about ``Security vs. Security'' than ``Security vs. Privacy''
\cite{stalla_bourdillon_privacy_2014}. In this context, there are two types of security: public security, the pursuit of
law enforcement, and cybersecurity, the pursuit of the technical community. Both sides of the debate have by now
acknowledged that privacy and public security are not always in conflict, and in fact \ac{EA}'s effects on public
security vs. cybersecurity---which in return affects public security---may be more important \cite{schneier_2019}.

@@

% FIXME: Engelsma: Consider moving this right after "encryption basics", as I have referred to many of these approaces
% already.

@@

% TODO: include a more descriptive key to understand argument maps.

% - Prof. Dulimarta: Could you apply fuzzy logic to the argument map? Quantify it? -- I think this would run into limits
%   once you start comparing unquantifiable things, but it could be used to suss out the valid arguments, and would
%   probably be really interesting otherwise.

### 2020-11-24 Thesis-Chapter5-ThreatModel.tex
Editorial updates
Updates based on presentation feedback

@@

The \ac{UID} is not depicted in key storage because it is actually burned into the secure processor silicon, and cannot
be read by software. The Volume key is stored encrypted by the Class key. When a user updates his \ac{PIN}, the
encrypted Volume key in storage is replaced with the copy encrypted with the new Class key. Application processors never
handle any keys or secret information besides the \ac{PIN}, and due to inline encryption in the Encryption Module,
persistent storage never handles and \ac{plaintext} data.

@@

The lawful access use case operates as follows: law enforcement obtains a warrant to conduct a search, including the
suspect's mobile device. They obtain the phone, disassemble it to expose the \ac{EA} hardware interface, and begin the
time-vaulted access request. After the lockout period is completed, the device offers its Device ID only. The law
enforcement agency's digital forensics department digitally signs the Device ID and sends it to the device vendor,
alongside the warrant and accompanying proof of legal authorization. The vendor's access compliance department audits
the legal documents and submits the digitally signed Device ID to a secure computing environment such as a \ac{HSM}. The
secure environment authenticates the digital signature, looks up the device's private Device Seal Key and authorization
token, and encrypts them with the law enforcement agency's public key. These encrypted artifacts are returned to the
agency, which decrypts and submits them to the device through the dedicated interface. First is the authorization token,
which is hashed and compared to the stored hash. If that values match, the device accepts and uses the private Device
Seal Key to decrypt the Class key, which was escrowed after being encrypted but the public Device Seal Key. Once the
Class key is decrypted, the escrow agent burns a fuse, and the device is unlocked for forensic investigation.

@@

To save space, the tables use shorthand for \acf{LE}, \acf{LEO}, \acf{LEA}, \acf{DID}, \acf{DSK}, and \acf{DOS}.

@@

\threattablebegin{Information Disclosure}{disclosure}{Information \\ Disclosed}
  I1 & Attacker exposes the DSK, DID, the encrypted class key, or hashed token
  & By design, none of the information stored on the phone is sensitive. The most consequential information that could
    be stolen is the DID, which could be paired with other attacks. Disclosing the DID requires either disassembly and
    time vaulting or advanced hardware inspection tooling.
  & Sensitivity of this data has already been mitigated as much as possible.
  \\ \hline
  I2 & Attacker intercepts unlock artifacts between LEA \ac{HSM} and device
  & The attacker is able to unlock the target device alone. Must be combined with a spoofed DID to be of use to other
    devices (see \ii{S2}). The attacker could record the values to replay them after the phone has been returned.
  & See \ii{S2}. If choosing not to destroy the device, to prevent replay attacks, a new token could be generated and
    stored in the vendor HSM, with the new hash installed during the unlock process.
  \\ \hline
  I3 & Attacker steals the LEA private key
  & The attacker is now able to spoof the LEA and decrypt returned unlock artifacts. Without the devices (which are
    already in LE possession), the artifacts are not useful. See \ii{S4} and \ii{S5} for LEA spoofing attacks.
  & The key is stored in an \ac{HSM}, which has extensive security measures. See \ii{S5} for a revocation and update
    mitigation.
  \\ \hline
  I4 & Attacker steals the DID-DSK database
  & This is the big prize, the largest source of centralized risk. With the database, attackers could directly
    compromise any mobile device using this system in their possession, after disassembly, and after the time vault.
    They may also try to sell access to the data.
  & \ii{R3} defines a mitigation that requires use of a vendor private key to create a digital signature as part of the
    authentication process. If used, that key would have to be compromised as well for the database to be of use.
    However, if the database is compromised, that key probably is too. Savage argues that \acp{HSM}, though imperfect,
    actually do provide very strong assurance. Responses could be rate-limited, and leaking an entire database once it's
    in the \ac{HSM} could not go unnoticed. Getting the data in may be harder---see \ii{I5}.
  \\ \hline
  I5 & Attacker steals device unlock artifacts between manufacturing and vendor \ac{HSM}
  & Intercepting the unlock artifacts at the source achieves the same effect as \ii{I4}, only the data set is not
    complete. Instead of granting the ability to unlock any device, including a specific target, this is suited for
    getting access down the line or for sale.
  & The unlock artifacts generation process must be treated as sensitively as the \ac{HSM} itself. The artifacts should
    be encrypted immediately and periodically transported to the corporate \ac{HSM} on physical media. This threat is
    difficult to definitively mitigate.
  \\ \hline
  I6 & Attacker steals device \ac{plaintext} from LEA after unlock process
  & Assuming the attacker doesn't care that the LEA gets access to plaintext, they could ``help'' the LE investigation
    in order to access the data later either when it comes out as public evidence or through compromising the LEA
    itself. This may be useful to authoritarian regimes, foreign intelligence, and organized crime.
  & LEAs must have strong information security of their own. Disclosure of evidence is a natural side effect of
    prosecution, so LEAs must practice discretion in choosing which devices to unlock in case mere information discovery
    poses a great risk in itself.
\threattableend

@@

>>>>

% TODO: Dulimarta: only looking at iPhone DAR? -- So I have to make clear that we are limiting scope here

@@

The \ac{UID} is not depicted in key storage because it is actually burned into the secure processor silicon, and cannot
be read by software. The Volume key is stored encrypted by the Class key. When a user updates his \ac{PIN}, the
encrypted Volume key in storage is replaced with the copy encrypted with the new Class key. Application processors never
handle any keys or secret information besides the \ac{PIN}, and due to inline encryption in the Encryption Module,
persistent storage never handles any \ac{plaintext} data.

@@

The lawful access use case operates as follows: law enforcement obtains a warrant to conduct a search, including the
suspect's mobile device. They obtain the phone, disassemble it to reveal the unexposed \ac{EA} hardware interface, and
begin the time-vaulted access request. After the lockout period is completed, the device offers its Device ID only. The
law enforcement agency's digital forensics department digitally signs the Device ID and sends it to the device vendor,
alongside the warrant and accompanying proof of legal authorization. The vendor's access compliance department audits
the legal documents and submits the digitally signed Device ID to a secure computing environment such as a \ac{HSM}. The
secure environment authenticates the digital signature, looks up the device's private Device Seal Key and authorization
token, and encrypts them with the law enforcement agency's public key. These encrypted artifacts are returned to the
agency, which decrypts and submits them to the device through the dedicated interface. First is the authorization token,
which is hashed and compared to the stored hash. If that values match, the device accepts and uses the private Device
Seal Key to decrypt the Class key, which was escrowed after being encrypted but the public Device Seal Key. Once the
Class key is decrypted, the escrow agent burns a fuse, and the device is unlocked for forensic investigation.

@@

To save space, the tables use shorthand for \acf{LE}, \acf{LEO}, \acf{LEA}, \acf{HSM}, \acf{DID}, \acf{DSK}, and
\acf{DOS}.

@@

\threattablebegin{Information Disclosure}{disclosure}{Information \\ Disclosed}
  I1 & Attacker discloses the DSK, DID, the encrypted class key, or hashed token
  & By design, none of the information stored on the phone is sensitive. The most consequential information that could
    be stolen is the DID, which could be paired with other attacks. Disclosing the DID requires either disassembly and
    time vaulting or advanced hardware inspection tooling.
  & Sensitivity of this data has already been mitigated as much as possible.
  \\ \hline
  I2 & Attacker intercepts unlock artifacts between LEA \ac{HSM} and device
  & The attacker is able to unlock the target device alone. Must be combined with a spoofed DID to be of use to other
    devices (see \ii{S2}). The attacker could record the values to replay them after the phone has been returned.
  & See \ii{S2}. If choosing not to destroy the device, to prevent replay attacks, a new token could be generated and
    stored in the vendor HSM, with the new hash installed during the unlock process.
  \\ \hline
  I3 & Attacker steals the LEA private key
  & The attacker is now able to spoof the LEA and decrypt returned unlock artifacts. Without the devices (which are
    already in LE possession), the artifacts are not useful. See \ii{S4} and \ii{S5} for LEA spoofing attacks.
  & The key is stored in an \ac{HSM}, which has extensive security measures. See \ii{S5} for a revocation and update
    mitigation.
  \\ \hline
  I4 & Attacker steals the DID-DSK database
  & This is the big prize, the largest source of centralized risk. With the database, attackers could directly
    compromise any mobile device using this system in their possession, after disassembly, and after the time vault.
    They may also try to sell access to the data.
  & \ii{R3} defines a mitigation that requires use of a vendor private key to create a digital signature as part of the
    authentication process. If used, that key would have to be compromised as well for the database to be of use.
    However, if the database is compromised, that key probably is too. Savage argues that \acp{HSM}, though imperfect,
    actually do provide very strong assurance. Responses could be rate-limited, and leaking an entire database once it's
    in the \ac{HSM} could not go unnoticed. Getting the data in may be harder---see \ii{I5}.
  \\ \hline
  I5 & Attacker steals device unlock artifacts between manufacturing and vendor \ac{HSM}
  & Intercepting the unlock artifacts at the source achieves the same effect as \ii{I4}, only the data set is not
    complete. Instead of granting the ability to unlock any device, including a specific target, this is suited for
    getting access down the line or for sale.
  & The unlock artifacts generation process must be treated as sensitively as the \ac{HSM} itself. The artifacts should
    be encrypted immediately and periodically transported to the corporate \ac{HSM} on physical media. This threat is
    difficult to definitively mitigate.
  \\ \hline
  I6 & Attacker steals device \ac{plaintext} from LEA after unlock process
  & Assuming the attacker doesn't care that the LEA gets access to plaintext, they could ``help'' the LE investigation
    in order to access the data later either when it comes out as public evidence or through compromising the LEA
    itself. This may be useful to authoritarian regimes, foreign intelligence, and organized crime.
  & LEAs must have strong information security of their own. Disclosure of evidence is a natural side effect of
    prosecution, so LEAs must practice discretion in choosing which devices to unlock in case mere information discovery
    poses a great risk in itself.
\threattableend

@@

% TODO: Platform abuser destroys the unlock artifacts database through physical attack

### 2020-11-24 Thesis-Chapter6-PathsAhead.tex
Editorial updates
Updates based on presentation feedback

These are not strong conclusions. However, when dealing with \acp{wicked-prob}, meaningful debate and discussion counts
as progress even when it doesn't seem like it. \Acp{wicked-prob} cannot be analyzed into resolution; grasping the
problem alone constitutes much of the work towards solving it. The conclusions above do not bring closure, but they
should bring more clarity, and its clarity that counts.

@@

The technical community needs to accept and deal with the enormous role technology is playing in current policy issues,
such as encryption, automation, and misinformation. Government sometimes suggests that the tech world is is not trying
hard enough, and that ``nerding harder'' will result in solutions. The tech world is absolutely right that nerding
harder will not work on these issues---because they are \acp{wicked-prob}---but that does not mean they cannot deal with
them. Tech is used to addressing tame problems, but it is time that they turn their massive financial and intellectual
capital towards strategies designed for \acp{wicked-prob}. This means including people of diverse experiences,
backgrounds, and values in decision making processes that steer investment and design decisions. It means creating
products and business models that are responsive to evolving conditions. It means considering the ways their creations
will be abused.

@@

>>>>

% FIXME: "The conclusions I draw do not settle the issue..." Make sure wording is good.

The conclusions I draw do not settle the issue. However, when dealing with \acp{wicked-prob}, meaningful debate and
discussion counts as progress even when it doesn't seem like it. \Acp{wicked-prob} cannot be analyzed into resolution;
grasping the problem alone constitutes much of the work towards solving it. The conclusions above do not bring closure,
but they should bring more clarity, and its clarity that counts.

@@

The technical community needs to accept and deal with the enormous role technology is playing in current policy issues,
such as encryption, automation, and misinformation. Government sometimes suggests that the tech world is not trying hard
enough, and that ``nerding harder'' will result in solutions. The tech world is absolutely right that nerding harder
will not work on these issues---because they are \acp{wicked-prob}---but that does not mean they cannot deal with them.
Tech is used to addressing tame problems, but it is time that they turn their massive financial and intellectual capital
towards strategies designed for \acp{wicked-prob}. This means including people of diverse experiences, backgrounds, and
values in decision making processes that steer investment and design decisions. It means creating products and business
models that are responsive to evolving conditions. It means considering the ways their creations will be abused.

@@

% Prof. Walsh:
% - Liked the lessons for techies; this distills the same problems for policymakers
% - Enjoyed perspective of the "hawkish lawmaker" and how that connects to LAED Act and fallacious argmap
% - Would love to see this in the conclusion -- tie it all together and make sure it hits home for policymakers
